Intensity Modulated Radiation Therapy using Tomotherapy

### 2014-12-08 BME 560/Paper.tex
Updates

  Table \ref{tab:compare} highlights the key differences in various systems. 
  For the 
  sake the completeness, the authors of Ref. \cite{Fenwick2006} have 
  dicotomized the conventional system into 2 types, with and without a 
  multileaf collimator, and the tomotherapy into serial and parallel 
  tomotherapy.
  \section{Clinical Applications}
  \label{clinical}
  This section highlights few of the many clinical applications of tomotherapy. 
  \subsection{Total Body Irradiation (TBI)}
  Tomotherapy can be used in establishing total body irradiation (TBI) to gain 
  greater control over the dose distribution and to spare organs that may be at 
  risk.

  One of the disadvantages of using Helical Tomography (HT) for TBI is that it 
  can't be used when the body length of the patient exceeds 145 cms. For 
  patients who are taller than this, a better solution needs to be deviced.
  \subsection{Whole brain helical Tomotherapy}
  \subsection{Inoperable Lung Cancer}
  \subsection{Rectal Cancer}
  \section{Conclusion}
  \label{conclusions}
  \bibliography{Paper}{}
  \bibliographystyle{IEEEtran}

>>>>

  Table \ref{tab:compare} highlights the key differences in various systems. 
  For the 
  sake the completeness, the authors of Ref. \cite{Fenwick2006} have 
  dicotomized the conventional system into 2 types, with and without a 
  multileaf collimator, and the tomotherapy into serial and parallel 
  tomotherapy.
  \section{Clinical Applications}
  \label{clinical}
  This section highlights few of the many clinical applications of tomotherapy. 
  \subsection{Total Body Irradiation (TBI)}
  Tomotherapy can be used in establishing total body irradiation (TBI) to gain 
  greater control over the dose distribution and to spare organs that may be at 
  risk. It was shown in Ref. \cite{Gruen2013} that using HT provided excellent 
  conformal 
  lung sparing with mean doses not exceeding 10 Gy. No lung toxicity was 
  observed for over 15 months after follow-up. Also, the overall morbidity 
  during the treatment period was very low, corresponding to grades 1-2 side 
  effects.

  In general the use of HT was effective in that it provided excellent 
  individual sparing of organs and very little side effects. There are still 
  room for improvements as one of the disadvantages of using Helical Tomography 
  (HT) for TBI is that it 
  can't be used when the body length of the patient exceeds 145 cms. Although 
  this makes it very effective in cases of pediatric oncology, for 
  patients who are taller than this, a better solution needs to be deviced.

  \subsection{Whole brain helical Tomotherapy}
  \subsection{Inoperable Lung Cancer}
  \subsection{Rectal Cancer}
  \section{Conclusion}
  \label{conclusions}
  \bibliography{Paper}{}
  \bibliographystyle{IEEEtran}
